### 2022-08-07 chapters/optimization/python-dir/python_interperters.tex
trim energy values

\section{placeholder}
we performed a shapiro normality test for the first on the results, and almost all the p-values smaller than alpha=0.01\% therefore the distrubution is not normal

@@

    \label{table:bitops}
    \begin{tabular}{|lrrrrr|}
        \toprule
        benchmark    & A          & GG         & LL         & Or         & XOR        \\
        \midrule
        activepython & 676.980672 & 763.208040 & 651.783048 & 743.016425 & 728.828481 \\
        cpython2     & 441.082298 & 435.886950 & 430.846171 & 415.247383 & 419.081447 \\
        cpython3     & 595.209019 & 685.085315 & 563.839300 & 657.972734 & 655.560574 \\
        cython       & 35.077408  & 182.688395 & 274.177830 & 34.868014  & 34.504778  \\
        nuitka       & 33.260991  & 32.980380  & 33.256450  & 33.472770  & 33.030889  \\
        numba2       & 9.102939   & 8.411176   & 9.460620   & 9.375920   & 9.755952   \\
        numba3       & 9.566646   & 10.144212  & 9.219703   & 9.344613   & 9.665108   \\
        pypy2        & 8.456867   & 7.844918   & 8.286278   & 8.138692   & 7.952999   \\
        pypy3        & 7.552731   & 8.093884   & 8.108508   & 8.669448   & 8.623737   \\
        shedskin     & 8.024198   & 8.070870   & 8.399917   & 8.126236   & 8.277546   \\
        \bottomrule
    \end{tabular}
    \vfill
    \centering
    \includegraphics[width=\linewidth]{imgs/bitopts_mean}
    \caption{energy consumption of different impelementations using Bit Operation benchmarks (Joule) }
\end{figure}

>>>>

\subsection{Preliminary stduies}
This part will be dedicated to analyse the initial behaviour of different python interpereters.
First we started with a typical benchmark \em binarrytree. where we compare the energy consumption of the different implementations.

\section{placeholder}

we performed a shapiro normality test for the first on the results, and almost all the p-values smaller than alpha=0.01\% therefore the distrubution is not normal

@@

    \label{table:bitops}
    \begin{tabular}{|lrrrrr|}
        \toprule
        benchmark    & A       & GG      & LL      & Or      & XOR     \\
        \midrule
        activepython & 676.980 & 763.208 & 651.783 & 743.016 & 728.828 \\
        cpython2     & 441.082 & 435.886 & 430.846 & 415.247 & 419.081 \\
        cpython3     & 595.209 & 685.085 & 563.839 & 657.972 & 655.560 \\
        cython       & 35.077  & 182.688 & 274.177 & 34.868  & 34.504  \\
        nuitka       & 33.260  & 32.980  & 33.256  & 33.472  & 33.030  \\
        numba2       & 9.102   & 8.411   & 9.460   & 9.375   & 9.755   \\
        numba3       & 9.566   & 10.144  & 9.219   & 9.344   & 9.665   \\
        pypy2        & 8.456   & 7.844   & 8.286   & 8.138   & 7.952   \\
        pypy3        & 7.552   & 8.093   & 8.108   & 8.669   & 8.623   \\
        shedskin     & 8.024   & 8.070   & 8.399   & 8.126   & 8.277   \\
        \bottomrule
    \end{tabular}
    \vfill
    \centering
    \includegraphics[width=\linewidth]{imgs/bitopts_mean}
    \caption{energy consumption of different impelementations using Bit Operation benchmarks (Joule) }
\end{figure}
